Target Markdown

### 2024-08-14 _targets.Rmd
Plotting methods

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_doak_eff_tab_csc_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      p_sem_tot_stab +
        theme(
          legend.position = "none",
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_doak.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      p_sem_tot_stab +
        guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto"
  )
  ),
  tar_target(p_sem_fig_file,
    ggsave_multiple(
      paste0("p_sem_fig", c(".png", ".pdf")),
      plot = p_sem_fig,
      path = here::here("report", "figures"),
      scale = 3.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm")
  ),
  tar_target(p_sem_tot_stab_file,
    ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

@@

```{r plot-sim}
load(here("data", "sim_for_plot"))
length(unique(sim_for_plot$sim_id))
sim_for_plot %<>%
  left_join(
    tar_read(sim_fw)
  )
stoch <- 0.3
hill <- 2
env_corr <- 0
label_var <- c("w_avg_tlvl", "stab_com", "pop_stab", "async", "sae_total", "cpe")
unique(sim_for_plot$env_stoch)
```

>>>>

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_doak_eff_tab_csc_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      p_sem_tot_stab +
        theme(
          legend.position = "none",
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_doak.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      p_sem_tot_stab +
        guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            text = element_text(size = 20),
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto", hjust = -.7, vjust = 1.7
  )
  ),
  tar_target(p_sem_fig_file,
    ggsave_multiple(
      paste0("p_sem_fig", c(".png", ".pdf")),
      plot = p_sem_fig,
      path = here::here("report", "figures"),
      scale = 3.4,
      dpi = 400,
      width = 80,
      height = 80 * 1,
      units = "mm")
  ),
  tar_target(p_sem_tot_stab_file,
    ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

@@

```{r plot-sim}
sim_for_plot <- readRDS(here("data", "sim_for_plot"))
length(unique(sim_for_plot$sim_id))
sim_for_plot %<>%
  left_join(
    tar_read(sim_fw_csc_rerun)
  )
stoch <- 0.3
hill <- 2
env_corr <- 0
label_var <- c("w_avg_tlvl", "stab_com", "pop_stab", "async", "sae_total", "cpe")
unique(sim_for_plot$env_stoch)
```
